Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
simulate for one individual with multiple runs

a <- sim_seeds(m.prms = m_1[1])
summ_seeds(a)
```

>>>>

# a <- sim_seeds(m.prms = m_1[1])
# summ_seeds(a)
```

Run a simulation for one individual, multiple runs, display animal movement, seed dispersal and print summary for all runs
```{r message=FALSE}

df <- NULL
summ.df <- NULL

for(j in 1:1){
  for(k in 1:3){
    a <- sim_seeds(m.prms = m_1[j]) %>% 
      mutate(indiv = as.factor(j),
             run = paste0("r_",k))

    b <- summ_seeds(a) %>% 
      mutate(indiv = as.factor(j),
             run = paste0("r_",k))

    df <- rbind.data.frame(df, a) 
    summ.df <- rbind.data.frame(summ.df, b) 
}
}

df %>% 
  ggplot(., aes(x = xloc, y=yloc, 
                #group = run,
                color = indiv)) +
  facet_wrap(~run) +
  geom_path() +
  scale_color_manual(values = mycols) +
  geom_point(data = df %>% drop_na(s.id), 
             aes(x = xloc, y = yloc)) +
  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
  theme_bw()
```
